The K2 Bright Star Survey

### 2019-05-17 paper/ms.tex
bedding abstract

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio. By considering the unsaturated scattered light `halo' around these stars we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that generalizations of Total Variation perform well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
While the \kepler\ Mission was designed to look at tens of thousands of faint stars ($V \gtrsim 12$), brighter stars, which saturate the detector, are important because they can be and have been observed by other instruments at very high signal-to-noise ratio. By analyzing the unsaturated scattered-light `halo' around these stars, we can and do retrieve precise light curves of most of the brightest stars in \ktwo fields from Campaign~4 onwards. The halo method is highly agnostic about the cause and form of systematics and we show that it nevertheless it is effective at extracting light curves from both normal and saturated stars. The key methodology is to optimize the weights of a linear combination of pixel time series with respect to an objective function. We test a range of such objective functions, finding that generalizations of Total Variation perform well on both saturated and unsaturated \ktwo targets. Applying this to the bright stars across the \ktwo Campaigns, this reveals stellar variability ubiquitously, including effects of stellar pulsation, rotation, and binarity. Here we describe our pipeline, and present a catalogue of the bright stars studied, with classifications and parametrizations of their variability and remarks on interesting objects. These light curves are publicly available as a High Level Science Product from the Mikulski Archive for Space Telescopes (MAST). \href{https://github.com/benjaminpope/k2halo}{\color{linkcolor}\faGithub} % git link shamelessly borrowed from Luger!
\end{abstract}
